---
title: "carbon footprint perceptions results pilot"

date: "`r Sys.Date()`"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: 4
    number_sections: no

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "CSSoutput",
                      eval = TRUE, echo = FALSE, include = TRUE,warning=FALSE,
                      fig.align='center', fig.show='asis', fig.width = 16, fig.height = 10,
                      size='footnotesize')

```

```{r packages, include=FALSE}
getwd()

library(tidyverse)
library(sjPlot)
library(rcompanion)
library(rstatix)
library(lmerTest); library(lme4)
library(sjlabelled)
library(sjmisc)
library(emmeans)
library("rmcorr")
library(psych)
library(patchwork)
library(afex)
library(ClinSigMeasures)
library(prettydoc)
library(ggeffects)
library(reghelper) # for simple slopes
library(interactions)# for simple slopes

library("rmcorr")
library(Hmisc)
library(corrplot)
library(ggcorrplot)
library(ircor)

library(GPArotation)
set_theme(base=theme_classic())
# so plot_model plots look nice
set_theme(base=theme_classic())
```



```{r data, include=FALSE}
data <- read.csv("data/data.all_variables.csv")
data <- na.omit(data)

data$age.control <- 2023 - data$age_year
data$age.control2 <- 2022- data$age_year
data$age.control.f <- ifelse(between(data$age, data$age.control2, data$age.control ), "okay", "no")

data.excl <- data %>% select(age.control.f, participant.label) %>% filter(age.control.f=="no")

data.policies.long <- read.csv("data/data.policies.long.csv")
data.policies.long$support.f <- factor(data.policies.long$support.f)
data.policies.long$type <- factor(data.policies.long$type)
data.policies.long$policy2 <- factor(data.policies.long$policy,
                                    levels=c("subsidies alternative flying", "expand public transport", "subsidies RE projects", "subsidies low emission foods","subsidies regional food", "expand recycling",   
                                             "taxes air travel","ban diesel&petrol cars",  "electricity price peak times", "taxes red meat", "taxes imported food",   "taxes non-recylabes"))

data.policies.long <- data.policies.long[!c(data.policies.long$participant.label %in% data.excl$participant.label), ] 
data.policies.long$income <- factor(data.policies.long$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.regression.weights <- read.csv("data/data.regression.weights.csv")
data.regression.weights <- data.regression.weights[!c(data.regression.weights$participant.label %in% data.excl$participant.label), ] 
data.regression.weights$income <- factor(data.regression.weights$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.accuracy.score.tau <- read.csv("data/data.accuracy.score.tau.csv")
data.accuracy.score.tau <- data.accuracy.score.tau[!c(data.accuracy.score.tau$participant.label %in% data.excl$participant.label), ] 
data.accuracy.score.tau$income <- factor(data.accuracy.score.tau$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))
data.accuracy.score.tau$rel_cc_concern.mean.f <- factor(data.accuracy.score.tau$rel_cc_concern.mean.f)
data.accuracy.score.tau$rel_cor.tau.f <- factor(data.accuracy.score.tau$rel_cor.tau.f)

data.accuracy.score <- read.csv("data/data.accuracy.score.csv")
data.accuracy.score <- data.accuracy.score[!c(data.accuracy.score$participant.label %in% data.excl$participant.label), ] 


data.perceptions.total <- read.csv("data/data.perceptions.total.csv")
data.perceptions.total <- data.perceptions.total[!c(data.perceptions.total$participant.label %in% data.excl$participant.label), ] 
data.perceptions.total$income <- factor(data.perceptions.total$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.perceptions.total$flying <- factor(data.perceptions.total$flying, 
                                        levels=c("takes train (does not fly)", "flies 2/year"))
data.perceptions.total$diet <- factor(data.perceptions.total$diet, 
                                        levels=c("vegetarian", "meat-based"))
data.perceptions.total$electricity <- factor(data.perceptions.total$electricity, 
                                     levels=c("100% renewable energy supply", "mixed energy supply"))
data.perceptions.total$commute <- factor(data.perceptions.total$commute, 
                                     levels=c("take the bike", "takes the bus"))
data.perceptions.total$regional <- factor(data.perceptions.total$regional, 
                                         levels=c("only regional", "regional and imported"))
data.perceptions.total$recycling <- factor(data.perceptions.total$recycling, 
                                          levels=c("recycles", "does not recycle"))




```



## Overview and descriptives


### cc concern
```{r plot.ccc, echo=FALSE, message=FALSE}

## cc concern

data.cc_concern <-data %>% select(participant.label, climate_change_concern1,climate_change_concern2,climate_change_concern3,climate_change_concern4, cc_concern.mean, conservative_liberal.binary)
data.cc_concern <- na.omit(data.cc_concern)
data.cc_concern.long <- pivot_longer(data.cc_concern, climate_change_concern1:climate_change_concern4, names_to = "item", values_to = "cc.concern")

data.cc_concern.long$cc.concern.f <- factor(data.cc_concern.long$cc.concern)
 
ggplot(data.cc_concern.long,aes( x=item, fill=cc.concern.f), group=item) +
  geom_bar( position="dodge") + facet_grid(conservative_liberal.binary ~.) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 14), 
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=14, angle=90 ),
        strip.text = element_text(size=14))  +
  scale_fill_viridis_d()

tapply(data$cc_concern.mean, data$conservative_liberal.binary, mean)

```


### Policy support
Alpha= 0.87
```{r plot.policy, echo=FALSE, message=FALSE}
## visualizing
data.policies.long2 <- data.policies.long %>% filter(!policy2=="expand recycling") %>% filter(!policy2=="taxes non-recylabes")
ggplot(data.policies.long2,aes( x=policy2, fill=support.f), group=type) +
  geom_bar( position="dodge") + 
  theme_minimal() +
  theme(axis.title  = element_text(size = 14), 
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=14, angle=90 ),
        strip.text = element_text(size=14))  +
  scale_fill_viridis_d()


## means
data.policy.means <- groupwiseMean(support ~ policy2 + conservative_liberal.binary,
                                   data=data.policies.long2)
# midpoint would be 4
ggplot(data.policy.means,aes( x=policy2, y=Mean, fill=policy2) )+
  geom_bar( position="dodge", stat="identity") + 
  facet_grid(conservative_liberal.binary ~.) +
  geom_errorbar(aes(ymin=Trad.lower, ymax=Trad.upper), position=position_dodge(0.9), width=0.1) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 14), 
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=14, angle=90 ),
        strip.text = element_text(size=14))  +
  scale_fill_viridis_d() + ylim(0,7.5) + 
  geom_abline(slope=0, intercept=4,linetype="dashed" )
  labs(x="policies", y="Mean support", fill=NULL)

```

```{r, include=FALSE}

## basics, reliability etc
psych::alpha(data[c("policy_item1" ,"policy_item11" ,  "policy_item3", "policy_item5" , "policy_item8", 
                             "policy_item12",  "policy_item2", "policy_item4" , "policy_item6",  "policy_item7" )])

# alpha = 0.87
#item 10 (expand recyling) , item9 taxes on non-recyclables
# "subscaling" subsidies = 0.79
#psych::alpha(data[c("policy_item1" ,"policy_item11" ,  "policy_item3", "policy_item5" , "policy_item8")])
# "subscaling" taxes = 0.89
#psych::alpha(data[c( "policy_item12",  "policy_item2", "policy_item4" , "policy_item6",  "policy_item7" )])

```

### Behaviors 

```{r}
corr.behaviors <- data.regression.weights %>% select(footprint.diet, footprint.regional, footprint.electricity, footprint.recycling, 
                                                     footprint.travel.car, footprint.flying, footprint.public.transport)
coef.behaviors <- rcorr(as.matrix(corr.behaviors))
corrplot(coef.behaviors$r, type="upper", order="hclust", 
         p.mat = NULL, sig.level = 0.05, insig = "blank")


```

```{r}
## factors

data.regression.weights <- data.regression.weights %>%
  mutate_at(vars(starts_with("footprint")), list(fact = function(x){ factor(x )  })) %>% 
  mutate(across(ends_with("fact"), as.factor) )

data.regression.weights$footprint.diet_fact <- factor(data.regression.weights$footprint.diet_fact, levels=c(0.955, 1.053 ,1.234 ,1.431, 2.282,  3.16),
                                                      labels=c("vegan", "vegetarian", "no red meat", "pescetarian", "meat-based", "no pork") )
data.regression.weights$footprint.flying_fact <- factor(data.regression.weights$footprint.flying_fact, levels=c( 0  ,0.36,   0.9  ,2.07,  3.59,  6.74, 13.48 ),
                                                      labels=c("did not fly", "flew less than 2 hours", "flew less than 8 hours", "flew less than 15 hours", "flew less than 25 hours", "flew less than 50 hours", "flew more than 50 hours") )

data.regression.weights$footprint.electricity_fact <- factor(data.regression.weights$footprint.electricity_fact, levels=c( 0.1031, 0.6988837 , 1.294697  ),
                                                      labels=c("have a renwable electricity supply", "have a mixed electricity supply", "have a conventional supply / dont know") )


corr.behaviors.fact <-data.regression.weights %>% select(ends_with("_fact")) %>% select(!footprint.public.transport_fact)

model.matrix(~0+., data=corr.behaviors.fact) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

```

```{r}
data.regression.weights.long <-  pivot_longer(data.regression.weights,flying.weight:recycling.weight, names_to = "behavior", values_to = "regression.weight" )

data.regression.weights.long$behavior.label <- factor(data.regression.weights.long$behavior, 
                                                levels=c("flying.weight", "diet.weight", "electricity.weight" ,"regional.weight", "commute.weight","recycling.weight" ) ,
                                                labels=c("train vs. flying 2/year", "diet vegetarian vs. omnivore", "100% RE vs. mixed",
                                                         "regional only vs imported food", "commute by bus vs. bike", "recycling vs. not")) 

ggplot(data.regression.weights.long, aes(x=reorder(behavior.label,-regression.weight), y=regression.weight, color=behavior.label)) +
  geom_boxplot() + 
  # facet_grid(conservative_liberal.binary~.) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 14), 
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=14, angle=90 ),
        strip.text = element_text(size=14),
        legend.position = "none")  +
  scale_color_viridis_d() + labs(fill=NULL)
```


### Description of typical participant
```{r}

data.behaviors.diet <- data.regression.weights %>% select(participant.label, footprint.diet_fact) %>% group_by(footprint.diet_fact) %>% tally()
data.behaviors.diet$perc <- round(data.behaviors.diet$n/199*100,1)


data.behaviors.flying <- data.regression.weights %>% select(participant.label, footprint.flying_fact) %>% group_by(footprint.flying_fact) %>% tally()
data.behaviors.flying$perc <- round(data.behaviors.flying$n/199*100,1)

data.behaviors.elec <- data.regression.weights %>% select(participant.label, footprint.electricity_fact) %>% group_by(footprint.electricity_fact) %>% tally()
data.behaviors.elec$perc <- round(data.behaviors.elec$n/199*100,1)

```
Most participants: `r paste0(data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="meat-based" ] , "%") ` follow a meat-based diet, `r paste0(data.behaviors.flying$perc[data.behaviors.flying$footprint.flying_fact=="did not fly" ] , "%") ` did not fly , 
and have a conventional electricity supply (or dont know): `r paste0(data.behaviors.elec$perc[data.behaviors.elec$footprint.electricity_fact=="have a conventional supply / dont know" ] , "%" ) `, whereas `r paste0(data.behaviors.elec$perc[data.behaviors.elec$footprint.electricity_fact=="have a renwable electricity supply"], "%") ` have a renewable electricity supply, and only `r paste0(data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="vegetarian" ] + data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="vegan" ], "%" )` are vegan or vegetarian    
  
    
    
  
## Hypothesis 1, 1a

*We will explore the accuracy of perceptions of the impact of different behaviors and domains on carbon footprints. Specifically, we expect that individuals will underestimate the effect of higher impact behavior (flying, diet, electricity supply) and underestimate the effect of relatively less impactful behaviors (recycling, public transport, imported foods) *
*We assume that the impact of behaviors and their domain has an impact on participants’ estimations of the size of carbon footprints. We specifically expect that high impact behaviors have a stronger weight on impact estimations compared to low impact behaviors. *

**Effect of high versus low impact behaviors **
```{r}
data.perceptions.total.long <- data.perceptions.total
data.perceptions.total.long$diet <-(as.numeric(data.perceptions.total.long$diet)-1)
data.perceptions.total.long$flying <- (as.numeric(data.perceptions.total.long$flying)-1)
data.perceptions.total.long$commute <- (as.numeric(data.perceptions.total.long$commute)-1)
data.perceptions.total.long$regional <- (as.numeric(data.perceptions.total.long$regional)-1)
data.perceptions.total.long$recycling <- (as.numeric(data.perceptions.total.long$recycling)-1)
data.perceptions.total.long$electricity <- (as.numeric(data.perceptions.total.long$electricity)-1)

data.perceptions.total.long1 <- data.perceptions.total.long%>% rowwise() %>% 
  mutate(high.impact= factor(sum(commute, regional, recycling), levels=c(0,1,2,3), labels=c("none", "1", "2", "all") )  ,
          low.impact = factor(sum(flying, diet,   electricity), levels=c(0,1,2,3), labels=c("none", "1", "2", "all") )  ,
         household = factor(sum( electricity, recycling), levels=c(0,1,2), labels=c("none", "1", "both") )   ,
         food =  factor(sum( diet,   regional), levels=c(0,1,2), labels=c("none", "1", "both") )   ,
         transport = factor(sum(flying, commute), levels=c(0,1,2), labels=c("none", "1", "both") )   )

model.perceptions.long.impact <- lmer(rating ~   high.impact + low.impact+  #household + food + transport +
                                   age + gender + income + education +

                            (1|participant.label) , #+ (1|vignette),
                          data=data.perceptions.total.long1)
tab_model(model.perceptions.long.impact)
plot_model(model.perceptions.long.impact, terms=c("high.impact [1,2,all]", "low.impact [1,2,all]" ))


```


```{r, include=FALSE}
model.perceptions.long.domain <- lmer(rating ~  high.impact +low.impact + food + transport +
                                   age + gender + income + education +

                            (1|participant.label) + (1|vignette),
                          data=data.perceptions.total.long1)
tab_model(model.perceptions.long.domain)
plot_model(model.perceptions.long.domain, terms=c("household [1,both]", "transport [1,both]", "food [1,both]" ))


```

**Effect of different behaviors **
```{r}
# order of impact in the choice task behaviors : vacation, diet, household, regional, commute, recylcing
model.perceptions1 <- lmer(rating ~ recycling + commute + regional + electricity +diet + flying +   
                             age + gender + income + education +
                            (1|participant.label) + (1|vignette),
                          data=data.perceptions.total)
tab_model(model.perceptions1)
plot_model(model.perceptions1)



```


## H1b Compensatory Beliefs
*We expect that perceptions of the size of carbon footprints are influenced by interactions between behaviors. Specifically, we will investigate the interactions between: diet and regionality, diet and electricity supply, diet and flying, flying and commuting*

```{r comp}
#diet and regionality, diet and electricity supply, diet and flying, flying and commuting
model.perceptions.comp <- lmer(rating ~ diet*flying + diet*electricity + diet*regional + commute  + recycling +
                            age + gender + education +
                            (1|participant.label),
                          data=data.perceptions.total)

tab_model(model.perceptions.comp)
```

### Diet and flying
```{r comp1}
#diet and regionality, diet and electricity supply, diet and flying, flying and commuting
model.perceptions.comp1 <- lmer(rating ~ diet*flying+electricity +regional + commute  + recycling +
                            age + gender + education +
                            (1|participant.label),
                          data=data.perceptions.total)

tab_model(model.perceptions.comp1)
plot_model(model.perceptions.comp1, type="pred", terms=c("diet", "flying"))

```

### For other interactions no evidence of compensatory beliefs {.tabset}

#### Diet and regional
```{r comp3}
model.perceptions.comp3 <- lmer(rating ~ diet + flying + electricity + diet*regional  + commute  + recycling +
                            age + gender + education +
                            (1|participant.label),
                          data=data.perceptions.total)

tab_model(model.perceptions.comp3)
plot_model(model.perceptions.comp3, type="pred", terms=c("diet", "regional"))

```

#### diet and electricity supply
```{r comp2}

model.perceptions.comp2 <- lmer(rating ~ diet + flying + diet*electricity +regional  + commute  + recycling +
                            age + gender + income + education +
                            (1|participant.label),
                          data=data.perceptions.total)

tab_model(model.perceptions.comp2)
plot_model(model.perceptions.comp2, type="pred", terms=c("diet", "electricity"))

```


#### Flying and commute to work
```{r}


model.perceptions.comp4 <- lmer(rating ~ diet + flying + electricity + regional + flying*commute  + recycling +
                            age + gender + education +
                            (1|participant.label),
                          data=data.perceptions.total)

tab_model(model.perceptions.comp4)
plot_model(model.perceptions.comp4, type="pred", terms=c("flying", "commute"))
```


## H2 accuracy  {.tabset}
*H2: We expect to find an association between the accuracy of carbon footprint estimations and individuals' climate change concern, political orientation, carbon footprints based on reported behavior, and policy support. Specifically, we expect that individuals with more accurate perceptions are more likely to have lower carbon footprints and report higher policy support.*

### Predicting Accuracy 
```{r}
model.accuracy2 <- lm(cor.tau ~ age + gender + education + income +
                       cc_concern.mean + conservative_liberal + total_co2,
                     data=data.accuracy.score.tau)
tab_model(model.accuracy2)
ggplot(data.accuracy.score.tau, aes(x=cor.tau, fill=rel_cc_concern.mean.f, alpha=.3)) +
  geom_density() +
  theme_minimal() +
  scale_fill_manual(values=c(  "#a50000", "#ff8c00", "#F6BE00"))



```

### Policy support predicted by accuracy
```{r}
model.support.accuracy2 <- lm(policy.support.total ~ cor.tau+
                               age + gender + education + income +
                               cc_concern.mean ,
                             data=data.accuracy.score.tau)
tab_model(model.support.accuracy2)
ggplot(data.accuracy.score.tau, aes(x=policy.support.total, fill=rel_cor.tau.f, alpha=.3)) +
  geom_density() +
  theme_minimal() +
  scale_fill_manual(values=c(  "#a50000", "#ff8c00", "#F6BE00"))

model.support.accuracy2.mod <- lm(policy.support.total ~ cor.tau*cc_concern.mean+
                               age + gender + education + income ,
                             data=data.accuracy.score.tau)
#tab_model(model.support.accuracy2.mod)
# not significant with interaction

```



### Carbon footprint predicted by accuracy  {.tabset}
```{r}

model.behavior.accuracy2 <- lm(total_co2 ~ cor.tau + cc_concern.mean+ conservative_liberal +
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)
tab_model(model.behavior.accuracy2)

# cc concern also looses significance interaction


ggplot(data.accuracy.score.tau, aes(x=total_co2, fill=rel_cc_concern.mean.f, alpha=.3)) +
  geom_density() +
  theme_minimal() +
  scale_fill_manual(values=c(  "#a50000", "#ff8c00", "#F6BE00"))


# alpha/6 is 0.008333333
## for footprint.flying not significant (p ~0.86)
## for footprint.diet not significant when controlling for multiple tests (p  0.028)
## for footprint.travel.car not significant (p  0.07)
## for footprint.electricity not significant (p  0.459)

#data.accuracy.score.tau1 <- data.accuracy.score.tau %>% rename(policy = policy.car)
#data.accuracy.score.tau2 <- data.accuracy.score.tau %>% rename(policy = policy.flying)
#data.accuracy.score.tau3 <- data.accuracy.score.tau %>% rename(policy = policy.meat)
#data.accuracy.score.tau4 <- data.accuracy.score.tau %>% rename(policy = policy.RE)
#data.accuracy.score.tau5 <- data.accuracy.score.tau %>% rename(policy = policy.regional_food)

model.behavior.accuracy1.car <- lm(footprint.travel.car ~   cc_concern.mean+ conservative_liberal  + # policy+
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)
model.behavior.accuracy1.fly <- lm(footprint.flying ~   cc_concern.mean+ conservative_liberal  + # policy+
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)

model.behavior.accuracy1.diet <- lm(footprint.diet ~    cc_concern.mean+  conservative_liberal +  # policy+
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)

model.behavior.accuracy1.elec <- lm(footprint.electricity ~  +cc_concern.mean+ conservative_liberal +  # policy+
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)

model.behavior.accuracy1.reg <- lm(footprint.regional ~  cc_concern.mean+ conservative_liberal +  # policy+
                                age + gender + education + income ,
                              data=data.accuracy.score.tau)

```

```{r   echo=FALSE, message=FALSE, fig.width=25, fig.height=16}
plot_models( model.behavior.accuracy1.car, model.behavior.accuracy1.fly, model.behavior.accuracy1.diet,model.behavior.accuracy1.elec , model.behavior.accuracy1.reg, dot.size = 5, line.size=1.2, show.p = TRUE, p.shape=TRUE, p.threshold = c(0.05, 0.05/6), rm.terms=c("income [18.000£ to 23.000£, 23.001£ to 30.500£, 0.501£ to 45.000£]","education [Further education, Higher education (Bachelor, Master, PhD)]") ) +
  scale_color_viridis_d() + theme_minimal()+
   theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 25, face = "bold",family = 'Arial', color="black"),
          axis.title  = element_text(size = 25, family = 'Arial', color="black"),
          axis.text = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.y = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.x = element_text(size = 23, family = 'Arial', color="black"),
          legend.title = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          strip.text = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          legend.text = element_text(size = 22,family = 'Arial', color="black")) 
```


#### car
```{r}
tab_model(model.behavior.accuracy1.car)

```

#### flying
```{r}
tab_model(model.behavior.accuracy1.fly)

```

#### diet
```{r}
tab_model(model.behavior.accuracy1.diet)

```

#### electricity
```{r}
tab_model(model.behavior.accuracy1.elec)

```

#### regional
```{r}
tab_model(model.behavior.accuracy1.reg)

```

## H3 Impact perceptions (=Regression weights) predicted by reported behavior?

### Correlations between regression weights
```{r}

corr.regr.weights <- data.regression.weights %>% select(ends_with("weight"))
coef.reg.weights <- rcorr(as.matrix(corr.regr.weights))

corrplot(coef.reg.weights$r, type="upper", order="hclust", 
         p.mat = NULL, sig.level = 0.05, insig = "blank")

```

*We expect that the perceived impact of behaviors on the size of carbon footprints is influenced by self-reported climate relevant behavior. Specifically, we expect that individuals exhibit motivated reasoning such that the more a person engages in a given climate-unfriendly behavior, the lower they estimate the behavior to have an impact on the size of carbon footprints.*

## as factors {.tabset}

### Flying
```{r}


#data.regression.weights$footprint.flying_fact <- factor(data.regression.weights$footprint.flying_fact, levels=c("0" , "0.36", "0.9", "2.07",  "3.59",  "6.74", "13.48" ), labels=c("no flying", "under 7 hours", "under 7 hours","more than 7 hours", "more than 7 hours", "more than 7 hours",  "more than 7 hours") )
model.weight.flying.fact <- lm(flying.weight ~ footprint.flying_fact    + 
                            gender + age + income + education + cc_concern.mean,
                          data=data.regression.weights)
tab_model(model.weight.flying.fact)


```

### Diet
```{r}

# data.regression.weights$footprint.diet_fact.2 <- factor(data.regression.weights$footprint.diet_fact, levels=c("vegan", "vegetarian", "no red meat", "pescetarian", "meat-based", "no pork") , labels=c("reduction of meat", "reduction of meat", "reduction of meat", "reduction of meat", "meat-based", "meat-based"))

model.weight.diet.fact <- lm(diet.weight ~  footprint.diet_fact +
                         gender + age + income + education + cc_concern.mean,
                       data=data.regression.weights)
tab_model(model.weight.diet.fact)

```

### Electricity
```{r}
model.weight.diet.fact <- lm(electricity.weight ~  footprint.electricity_fact +
                         gender + age + income + education + cc_concern.mean,
                       data=data.regression.weights)
tab_model(model.weight.diet.fact)
```

### Commute
```{r}
model.weight.diet.fact <- lm(commute.weight ~  footprint.public.transport_fact +
                         gender + age + income + education + cc_concern.mean,
                       data=data.regression.weights)
tab_model(model.weight.diet.fact)
```



##  "numerical" {.tabset}


### Flying
```{r}
data.regression.weights.f <- data.regression.weights %>% rename(footprint=footprint.flying)

model.weight.flying <- lm(flying.weight ~ footprint +
                            gender + age + income + education + cc_concern.mean,
                          data=data.regression.weights.f)
tab_model(model.weight.flying)

```

### Diet
```{r}
data.regression.weights.d <- data.regression.weights %>% rename(footprint=footprint.diet)

model.weight.diet<- lm(diet.weight ~  footprint + 
                         gender + age + income + education + cc_concern.mean,
                       data=data.regression.weights.d)
tab_model(model.weight.diet)
```

### Electricity
```{r}
data.regression.weights.e <- data.regression.weights %>% rename(footprint=footprint.electricity)

model.weight.elec<- lm(electricity.weight ~  footprint +
                         gender + age + income + education + cc_concern.mean,
                       data=data.regression.weights.e)
tab_model(model.weight.elec)
```


### Transport
```{r}
data.regression.weights.t <- data.regression.weights %>% rename(footprint=footprint.public.transport)

model.weight.transport<- lm(commute.weight ~ footprint +
                              gender + age + income + education + cc_concern.mean,
                            data=data.regression.weights.t)
tab_model(model.weight.transport)

```

### Regional   

    
```{r}
data.regression.weights.reg <- data.regression.weights %>% rename(footprint=footprint.regional)

model.weight.regional<- lm(regional.weight ~footprint +
                       gender + age + income + education + cc_concern.mean,
                     data=data.regression.weights.reg)
tab_model(model.weight.regional)
```

### Recycling
```{r}
data.regression.weights.rec <- data.regression.weights %>% rename(footprint=footprint.recycling)

model.weight.recycle <- lm(recycling.weight ~footprint +
                       gender + age + income + education + cc_concern.mean,
                     data=data.regression.weights.rec)
tab_model(model.weight.recycle)
```

## Plot
```{r plot.weights,  echo=FALSE, message=FALSE, fig.width=25, fig.height=16}


plot_models(model.weight.flying, model.weight.diet, model.weight.elec, model.weight.transport,  model.weight.regional ,dot.size = 5, line.size=1.2, show.p = TRUE, p.shape=TRUE, p.threshold = c(0.05, 0.05/6) ) +
  scale_color_viridis_d() + theme_minimal()+
   theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 25, face = "bold",family = 'Arial', color="black"),
          axis.title  = element_text(size = 25, family = 'Arial', color="black"),
          axis.text = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.y = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.x = element_text(size = 23, family = 'Arial', color="black"),
          legend.title = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          strip.text = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          legend.text = element_text(size = 22,family = 'Arial', color="black")) 



```



## H4 Impact perceptions (=regression weights) predicting policy  {.tabset}

*We expect that climate policy support for specific consumer behaviors is influenced by the perceived impact of those behaviors on the size of carbon footprints. Specifically, we expect that individuals with higher (versus lower) impact perceptions of a behavior are more supportive of policies targeting that behavior. *

### Policy affecting air traffic

```{r}
### policy

data.regression.weights1 <- data.regression.weights %>% rename(weight=flying.weight)

model.policy.flying <- lm(policy.flying ~  weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                           data=data.regression.weights1)
tab_model(model.policy.flying)


```

### Policy affecting car use
```{r}
data.regression.weights2 <- data.regression.weights %>% rename(weight=commute.weight)

model.policy.car<- lm(policy.car ~  weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                          data=data.regression.weights2)
tab_model(model.policy.car)


```

### Diet
```{r}
data.regression.weights3 <- data.regression.weights %>% rename(weight=diet.weight)

model.policy.meat<- lm(policy.meat ~ weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                      data=data.regression.weights3)
tab_model(model.policy.meat)

```

### Policy electricity
```{r}
data.regression.weights4 <- data.regression.weights %>% rename(weight=electricity.weight)

model.policy.elec<- lm(policy.RE ~  weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                      data=data.regression.weights4)
tab_model(model.policy.elec)
```

### Policy regional
```{r}
data.regression.weights5 <- data.regression.weights %>% rename(weight=regional.weight)

model.policy.regional<- lm(policy.regional_food ~ weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                      data=data.regression.weights5)
tab_model(model.policy.regional)
```

### Policy recycling
```{r}
data.regression.weights6 <- data.regression.weights %>% rename(weight=recycling.weight)

model.policy.recycle<- lm(policy.recycle ~ weight +
                            cc_concern.mean+ conservative_liberal +
                            gender + age + income + education ,
                          data=data.regression.weights6)
tab_model(model.policy.recycle)
```

## Plot
```{r,  echo=FALSE, message=FALSE, fig.width=25, fig.height=16}
plot_models(model.policy.meat, model.policy.flying, model.policy.elec, model.policy.car,  model.policy.recycle, model.policy.regional ,dot.size = 5, line.size=1.2, show.p = TRUE, p.shape=TRUE, p.threshold = c(0.05, 0.05/6) )  +
  scale_color_viridis_d() +  theme_minimal()+
   theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 25, face = "bold",family = 'Arial', color="black"),
          axis.title  = element_text(size = 25, family = 'Arial', color="black"),
          axis.text = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.y = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.x = element_text(size = 23, family = 'Arial', color="black"),
          legend.title = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          strip.text = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          legend.text = element_text(size = 22,family = 'Arial', color="black")) 



```


## regression weights and behavior predicting policy {.tabset}


### Policy affecting air traffic

```{r}
### policy

data.regression.weights1.1 <- data.regression.weights %>% rename(weight=flying.weight,
                                                                 behavior = footprint.flying)

model.policy.flying.2 <- lm(policy.flying ~weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                           data=data.regression.weights1.1)
tab_model(model.policy.flying.2)


```

### Policy affecting car use
```{r}
data.regression.weights2.1 <- data.regression.weights %>% rename(weight=commute.weight,
                                                                   behavior = footprint.travel.car)

model.policy.car.2 <- lm(policy.car ~ weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                          data=data.regression.weights2.1)
tab_model(model.policy.car.2)


```

### Diet
```{r}
data.regression.weights3.1 <- data.regression.weights %>% rename(weight=diet.weight,
                                                                 behavior = footprint.diet)

model.policy.meat.2 <- lm(policy.meat ~ weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                      data=data.regression.weights3.1)
tab_model(model.policy.meat.2)

```

### Policy electricity
```{r}
data.regression.weights4.1 <- data.regression.weights %>% rename(weight=electricity.weight,
                                                                 behavior = footprint.electricity)

model.policy.elec.2 <- lm(policy.RE ~ weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                      data=data.regression.weights4.1)
tab_model(model.policy.elec.2)
```


### Policy regional
```{r}
data.regression.weights5.1 <- data.regression.weights %>% rename(weight=regional.weight,
                                                                 behavior= footprint.regional)

model.policy.regional.2 <- lm(policy.regional_food ~ weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                      data=data.regression.weights5.1)
tab_model(model.policy.regional.2)
```

### Policy recycling
```{r}
data.regression.weights6.1 <- data.regression.weights %>% rename(weight=recycling.weight,
                                                               behavior = footprint.recycling)

model.policy.recycle.2 <- lm(policy.recycle ~ weight   + behavior +
                        gender + age + income + education  + 
                          cc_concern.mean + conservative_liberal,
                      data=data.regression.weights6.1)
tab_model(model.policy.recycle.2)
```

### Plot
```{r,  echo=FALSE, message=FALSE, fig.width=20, fig.height=16}
plot_models(model.policy.meat.2, model.policy.flying.2, model.policy.elec.2, model.policy.car.2 ,dot.size = 5, line.size=1.2, show.p = TRUE, p.shape=TRUE, p.threshold = c(0.05, 0.01) )  +
  scale_color_viridis_d() + theme_minimal()+
   theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 25, face = "bold",family = 'Arial', color="black"),
          axis.title  = element_text(size = 25, family = 'Arial', color="black"),
          axis.text = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.y = element_text(size = 23, family = 'Arial', color="black"),
          axis.text.x = element_text(size = 23, family = 'Arial', color="black"),
          legend.title = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          strip.text = element_text(size = 22, face="plain",family = 'Arial', color="black"),
          legend.text = element_text(size = 22,family = 'Arial', color="black")) 



```



