---
pagetitle: "overview"

date: "`r Sys.Date()`"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: 4
    number_sections: no
    keep_md: yes

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "CSSoutput",
                      eval = TRUE, echo = FALSE, include = TRUE,warning=FALSE,
                      fig.align='center', fig.show='asis', fig.width = 16, fig.height = 10,
                      size='footnotesize')

```

```{r packages, include=FALSE}
getwd()

library(tidyverse)
library(sjPlot)
library(rcompanion)
library(rstatix)
library(lmerTest); library(lme4)
library(sjlabelled)
library(sjmisc)
library(emmeans)
library("rmcorr")
library(psych)
library(patchwork)
library(afex)
library(ClinSigMeasures)
library(prettydoc)
library(ggeffects)
library(reghelper) # for simple slopes
library(interactions)# for simple slopes
library(lmtest)

library("rmcorr")
library(Hmisc)
library(corrplot)
library(ggcorrplot)
library(ircor)

library(GPArotation)
set_theme(base=theme_classic())
# so plot_model plots look nice
set_theme(base=theme_classic())
```



```{r data, include=FALSE}
data <- read.csv("data/data.all_variables.csv")
data <- na.omit(data)

data$age.control <- 2023 - data$age_year
data$age.control2 <- 2022- data$age_year
data$age.control.f <- ifelse(between(data$age, data$age.control2, data$age.control ), "okay", "no")

data.excl <- data %>% select(age.control.f, participant.label) %>% filter(age.control.f=="no")

data.policies.long <- read.csv("data/data.policies.long.csv")
data.policies.long$support.f <- factor(data.policies.long$support.f)
data.policies.long$type <- factor(data.policies.long$type)
data.policies.long$policy2 <- factor(data.policies.long$policy,
                                    levels=c("subsidies alternative flying", "expand public transport", "subsidies RE projects", "subsidies low emission foods","subsidies regional food", "expand recycling",   
                                             "taxes air travel","ban diesel&petrol cars",  "electricity price peak times", "taxes red meat", "taxes imported food",   "taxes non-recylabes"))

data.policies.long <- data.policies.long[!c(data.policies.long$participant.label %in% data.excl$participant.label), ] 
data.policies.long$income <- factor(data.policies.long$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.regression.weights <- read.csv("data/data.regression.weights.new.csv")
data.regression.weights <- data.regression.weights[!c(data.regression.weights$participant.label %in% data.excl$participant.label), ] 

data.regression.weights$income <- factor(data.regression.weights$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))
data.regression.weights$rel.cc.concern <- scale(data.regression.weights$cc_concern.mean)[,1]
## factors
data.regression.weights <- data.regression.weights %>%
  mutate_at(vars(starts_with("footprint")), list(fact = function(x){ factor(x )  })) %>% 
  mutate(across(ends_with("fact"), as.factor) )

data.regression.weights$footprint.diet_fact <- factor(data.regression.weights$footprint.diet_fact, levels=c(0.955, 1.053 ,1.234 ,1.431, 2.282,  3.16),
                                                      labels=c("vegan", "vegetarian", "no red meat", "pescetarian", "meat-based", "no pork") )
data.regression.weights$footprint.flying_fact <- factor(data.regression.weights$footprint.flying_fact, levels=c( 0  ,0.36,   0.9  ,2.07,  3.59,  6.74, 13.48 ),
                                                      labels=c("did not fly", "flew less than 2 hours", "flew less than 8 hours", "flew less than 15 hours", "flew less than 25 hours", "flew less than 50 hours", "flew more than 50 hours") )

data.regression.weights$footprint.electricity_fact <- factor(data.regression.weights$footprint.electricity_fact, levels=c( 0.1031, 0.6988837 , 1.294697  ),
                                                      labels=c("have a renwable electricity supply", "have a mixed electricity supply", "have a conventional supply / dont know") )

data.accuracy.score.tau <- read.csv("data/data.accuracy.score.tau.csv")
data.accuracy.score.tau <- data.accuracy.score.tau[!c(data.accuracy.score.tau$participant.label %in% data.excl$participant.label), ] 

data.accuracy.score.tau$income <- factor(data.accuracy.score.tau$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))
data.accuracy.score.tau$rel_cc_concern.mean.f <- factor(data.accuracy.score.tau$rel_cc_concern.mean.f)
data.accuracy.score.tau$rel_cor.tau.f <- factor(data.accuracy.score.tau$rel_cor.tau.f)

data.accuracy.score <- read.csv("data/data.accuracy.score.csv")
data.accuracy.score <- data.accuracy.score[!c(data.accuracy.score$participant.label %in% data.excl$participant.label), ] 


data.perceptions.total <- read.csv("data/data.perceptions.total.csv")
data.perceptions.total <- data.perceptions.total[!c(data.perceptions.total$participant.label %in% data.excl$participant.label), ] 
data.perceptions.total$income <- factor(data.perceptions.total$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.perceptions.total$flying <- factor(data.perceptions.total$flying, 
                                        levels=c("takes train (does not fly)", "flies 2/year"))
data.perceptions.total$diet <- factor(data.perceptions.total$diet, 
                                        levels=c("vegetarian", "meat-based"))
data.perceptions.total$electricity <- factor(data.perceptions.total$electricity, 
                                     levels=c("100% renewable energy supply", "mixed energy supply"))
data.perceptions.total$commute <- factor(data.perceptions.total$commute, 
                                     levels=c("take the bike", "takes the bus"))
data.perceptions.total$regional <- factor(data.perceptions.total$regional, 
                                         levels=c("only regional", "regional and imported"))
data.perceptions.total$recycling <- factor(data.perceptions.total$recycling, 
                                          levels=c("recycles", "does not recycle"))

data.perceptions.total$rel.cc.concern <- scale(data.perceptions.total$cc_concern.mean)[,1]

data.importance.weights <- read.csv("data/data.importance.weights.csv")
data.importance.weights <- data.importance.weights[!c(data.importance.weights$participant.label %in% data.excl$participant.label), ] 
data.importance.weights$income <- factor(data.importance.weights$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))

data.part.worths <- read.csv("data/data.part.worths.csv")
data.part.worths <- data.part.worths[!c(data.part.worths$participant.label %in% data.excl$participant.label), ] 
data.part.worths$income <- factor(data.part.worths$income, levels=c("< 18.000£", "18.000£ to 23.000£", "23.001£ to 30.500£", "30.501£ to 45.000£", "> 45.001£"))


```

```{r}
## same response pattern??

data.perceptions.test <- pivot_wider(data.perceptions.total, id_cols = "participant.label" ,names_from ="vignette", values_from= "rating")
                                     

data.perceptions.test$same <- apply(data.perceptions.test[,c(2:17)], 1, function(x) length(unique(x)) <= 3)
#table(data.perceptions.test$same )
## only 8 people use only 3 of the scale points from 1-10, excluding these people has virtually no impact on results
data.perceptions.excl <- data.perceptions.test %>% filter(same=="FALSE" ) %>% select(participant.label)

data.perceptions.total.excl <- merge(data.perceptions.total, data.perceptions.excl, by="participant.label")

### exclude those with negative impact perceptions (because that makes 0 sense)
data.regression.weights.excl  <- data.regression.weights %>% filter(!diet.weight<0) %>%
  filter(!flying.weight<0) %>%  filter(!electricity.weight<0) %>%
  filter(!recycling.weight<0) %>%  filter(!commute.weight<0) %>% filter(!regional.weight<0)

### exclude those with negative accuracy score assoication because they are so bad that there is a negative correlation..
data.accuracy.score.tau.excl <- data.accuracy.score.tau %>% filter(!cor.tau<0) 

```



## Overview and descriptives
```{r}
t.gender <- table(data$gender)
t.income <- table(data$income)
```

Sample:  
N=196, (excluded n=3 out of 199 because of inconsistent response (age and year of birth do not match +-1)).  
Age: Mean: `r round( mean(data$age),1) `, range: `r range(data$age)`.  
gender: female: `r t.gender[[1]] ` ; male: `r t.gender[[2]] `  
income: 
```{r}
knitr::kable(t.income, align = "l", col.names = c("income", "Frequency"))
```

  
  
### Climate change concern
```{r plot.ccc,   message=FALSE}

## cc concern

data.cc_concern <-data %>% select(participant.label, climate_change_concern1,climate_change_concern2,climate_change_concern3,climate_change_concern4, cc_concern.mean, conservative_liberal.binary)
data.cc_concern <- na.omit(data.cc_concern)
data.cc_concern.long <- pivot_longer(data.cc_concern, climate_change_concern1:climate_change_concern4, names_to = "item", values_to = "cc.concern")

data.cc_concern.long$cc.concern.f <- factor(data.cc_concern.long$cc.concern)
 
ggplot(data.cc_concern.long,aes( x=item, fill=cc.concern.f), group=item) +
  geom_bar( position="dodge") + facet_grid(conservative_liberal.binary ~.) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18))  +
  scale_fill_viridis_d()

tapply(data$cc_concern.mean, data$conservative_liberal.binary, mean)

```


### Policy support
Alpha= 0.87
```{r plot.policy,   message=FALSE}
## visualizing
data.policies.long2 <- data.policies.long %>% filter(!policy2=="expand recycling") %>% filter(!policy2=="taxes non-recylabes")
ggplot(data.policies.long2,aes( x=policy2, fill=support.f), group=type) +
  geom_bar( position="dodge") + 
  theme_minimal() +
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18))  +
  scale_fill_viridis_d()


## means
data.policy.means <- groupwiseMean(support ~ policy2 + conservative_liberal.binary,
                                   data=data.policies.long2)
# midpoint would be 4
ggplot(data.policy.means,aes( x=policy2, y=Mean, fill=policy2) )+
  geom_bar( position="dodge", stat="identity") + 
  facet_grid(conservative_liberal.binary ~.) +
  geom_errorbar(aes(ymin=Trad.lower, ymax=Trad.upper), position=position_dodge(0.9), width=0.1) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18))  +
  scale_fill_viridis_d() + ylim(0,7.5) + 
  geom_abline(slope=0, intercept=4,linetype="dashed" ) +
  labs(x="policies", y="Mean support", fill=NULL)

```

```{r, include=FALSE}

## basics, reliability etc
#psych::alpha(data[c("policy_item1" ,"policy_item11" ,  "policy_item3", "policy_item5" , "policy_item8", 
 #                            "policy_item12",  "policy_item2", "policy_item4" , "policy_item6",  "policy_item7" )])

# alpha = 0.87
#item 10 (expand recyling) , item9 taxes on non-recyclables
# "subscaling" subsidies = 0.79
#psych::alpha(data[c("policy_item1" ,"policy_item11" ,  "policy_item3", "policy_item5" , "policy_item8")])
# "subscaling" taxes = 0.89
#psych::alpha(data[c( "policy_item12",  "policy_item2", "policy_item4" , "policy_item6",  "policy_item7" )])

```

### Reported Behaviors 
Correlation between reported behaviors
```{r}
corr.behaviors <- data.regression.weights %>% select(footprint.diet, footprint.regional, footprint.electricity, footprint.recycling, 
                                                     footprint.travel.car, footprint.flying, footprint.public.transport)
coef.behaviors <- rcorr(as.matrix(corr.behaviors))
corrplot(coef.behaviors$r, type="upper", order="hclust", 
         p.mat = NULL, sig.level = 0.05, insig = "blank")


```

```{r}
## factors


corr.behaviors.fact <-data.regression.weights %>% select(ends_with("_fact")) %>% select(!footprint.public.transport_fact)

model.matrix(~0+., data=corr.behaviors.fact) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

```

### Perceived impact

```{r}
data.regression.weights.long <-  pivot_longer(data.regression.weights,flying.weight:recycling.weight, names_to = "behavior", values_to = "regression.weight" )

data.regression.weights.long$behavior.label <- factor(data.regression.weights.long$behavior, 
                                                levels=c("flying.weight", "diet.weight", "electricity.weight" ,"regional.weight", "commute.weight","recycling.weight" ) ,
                                                labels=c("train vs. flying 2/year", "diet vegetarian vs. omnivore", "100% RE vs. mixed",
                                                         "regional only vs imported food", "commute by bus vs. bike", "recycling vs. not")) 

ggplot(data.regression.weights.long, aes(x=behavior.label, y=regression.weight, color=behavior.label)) +
  geom_boxplot() + 
  # facet_grid(conservative_liberal.binary~.) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18),
        legend.position = "none")  +
  scale_color_viridis_d() +
  labs(fill=NULL, x="behaviors in judgment task", y="perceived impact(regression weight)")
```
  
Quality check:  
Only 8 individuals show a reduced variance in their impact ratings, such that they  only use 3 or less of the scale points from 1-10. Excluding these people has virtually no impact on results.

### Part worths

```{r, fig.width=25, fig.height=18}
data.part.worths.long <-  pivot_longer(data.part.worths,flying.weight:recycling.weight, names_to = "behavior", values_to = "part.worths" )

data.part.worths.long$behavior.label <- factor(data.part.worths.long$behavior, 
                                                levels=c("flying.weight", "diet.weight", "electricity.weight" ,"regional.weight", "commute.weight","recycling.weight" ) ,
                                                labels=c("train vs. flying 2/year", "diet vegetarian vs. omnivore", "100% RE vs. mixed",
                                                         "regional only vs imported food", "commute by bus vs. bike", "recycling vs. not")) 

plot.PW <- ggplot(data.part.worths.long, aes(x=behavior.label, y=part.worths, color=behavior.label)) +
  geom_boxplot() + 
  # facet_grid(conservative_liberal.binary~.) +
  theme_minimal() + 
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18),
        legend.position = "none")  +
  scale_color_viridis_d() +
  labs(fill=NULL, x="behaviors in judgment task", y="Part worths", title="Part worths")
plot.PW
```

```{r, fig.width=25, fig.height=18}
data.part.worths.long.mean <- groupwiseMean(part.worths ~ behavior.label, data=data.part.worths.long)

behavior.label <- c("commutes by bus", "mixed electricity", "regional and imported food", "meat-based diet","does not recycle", "flies 2/year")
ggplot(data.part.worths.long.mean, aes(x= reorder(Mean, behavior.label), y= Mean, label =behavior.label)) +
    geom_col(position = "dodge", width = 0.5) + scale_x_discrete(labels= behavior.label) +
    theme_bw() + ylim(-0.5, 1.5) +
    labs(x=NULL, y="Part worths", color =NULL, fill =NULL) +
    theme(legend.position="bottom") +
    coord_flip()

## part worths refer to attribute levels -> higher scores in this case means influence more the perceived size of carbon footprints
# importance weights are overall the level of utlitiy / importance assigned to the attribute
```


## Importance weight

```{r, fig.width=25, fig.height=18}
data.importance.weights.long <-  pivot_longer(data.importance.weights,flying:recycling, names_to = "behavior", values_to = "importance.weight" )

data.importance.weights.long$behavior.label <- factor(data.importance.weights.long$behavior, 
                                                levels=c("flying", "diet", "electricity" ,"regional", "commute","recycling" ) ,
                                                labels=c("train vs. flying 2/year", "diet vegetarian vs. omnivore", "100% RE vs. mixed",
                                                         "regional only vs imported food", "commute by bus vs. bike", "recycling vs. not")) 

plot.IW <- ggplot(data.importance.weights.long, aes(x=behavior.label, y=importance.weight, color=behavior.label)) +
  geom_boxplot() + 
  # facet_grid(conservative_liberal.binary~.) +
  theme_minimal() +
  theme(axis.title  = element_text(size = 18), 
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size=18, angle=90 ),
        strip.text = element_text(size=18),
        legend.position = "none")  +
  scale_color_viridis_d() +
  labs(fill=NULL, x="behaviors in judgment task", y="Importance weight", title="Importance weights")
plot.IW

```


```{r, include=F}
# QUestion 4: Piechart-How many percent of the respondents think "very good", "good", "moderate", "bad" and "very bad" about the "less for more" project?



# Pie-chart (noch optimierungsfähig)
data.importance.weights.long.mean <- groupwiseMean(importance.weight ~ behavior.label, data=data.importance.weights.long)

#prop.table für die Häufigkeiten
M <- NULL
M$importance.weight <- data.importance.weights.long.mean$Mean
M$importance.weight <- round(M$importance.weight*100)
M$behavior <- data.importance.weights.long.mean$behavior.label

#Datenframe
Mdf <- data.frame(M)

#barplot
Mbp<- ggplot(Mdf, aes(x="", y=importance.weight, fill=behavior)) +
geom_bar(width = 1, stat = "identity")

```

```{r,fig.width=15, fig.height=15}
#Pie
Mpie <- Mbp + coord_polar("y", start=0)

#Pie verschönern (noch ausbaubar!)
Mpie +
    scale_fill_viridis_d(labels = c("Flying", "Diet", "Electricity", "Regional", "Commute", "Recycling"), alpha=0.4) + 
    labs(x = NULL, y = NULL, fill = "Behavior", title = NULL, alpha=NULL) + 
    geom_text(aes(label = round(importance.weight, 2)), 
              position = position_stack(vjust = 0.5),
              size=6,
              col="black") + 
    theme_void() 
```


### Description of typical participant
```{r}

data.behaviors.diet <- data.regression.weights %>% select(participant.label, footprint.diet_fact) %>% group_by(footprint.diet_fact) %>% tally()
data.behaviors.diet$perc <- round(data.behaviors.diet$n/196*100,1)


data.behaviors.flying <- data.regression.weights %>% select(participant.label, footprint.flying_fact) %>% group_by(footprint.flying_fact) %>% tally()
data.behaviors.flying$perc <- round(data.behaviors.flying$n/196*100,1)

data.behaviors.elec <- data.regression.weights %>% select(participant.label, footprint.electricity_fact) %>% group_by(footprint.electricity_fact) %>% tally()
data.behaviors.elec$perc <- round(data.behaviors.elec$n/196*100,1)

```
Most participants: `r paste0(data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="meat-based" ] , "%") ` follow a meat-based diet, `r paste0(data.behaviors.flying$perc[data.behaviors.flying$footprint.flying_fact=="did not fly" ] , "%") ` did not fly , 
and have a conventional electricity supply (or dont know): `r paste0(data.behaviors.elec$perc[data.behaviors.elec$footprint.electricity_fact=="have a conventional supply / dont know" ] , "%" ) `, whereas `r paste0(data.behaviors.elec$perc[data.behaviors.elec$footprint.electricity_fact=="have a renwable electricity supply"], "%") ` have a renewable electricity supply, and only `r paste0(data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="vegetarian" ] + data.behaviors.diet$perc[data.behaviors.diet$footprint.diet_fact=="vegan" ], "%" )` are vegan or vegetarian    
  
    
